\documentclass{beamer}

% \usepackage[lined,ruled]{algorithm2e}
\usepackage{subfigure}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc} 
\usepackage{color}

\usepackage{listings}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{paralist}

% "define" Scala
\lstdefinelanguage{scala}{
  morekeywords={abstract,case,catch,class,def,%
    do,else,extends,false,final,finally,%
    for,if,implicit,import,match,mixin,%
    new,null,object,override,package,%
    private,protected,requires,return,sealed,%
    super,this,throw,trait,true,try,%
    type,val,var,while,with,yield, textFile, filter, cache, count,
    flatMap, map, reduceByKey, saveAsTextFile},
  otherkeywords={=>,<-,<\%,<:,>:,\#,@, <+=},
  sensitive=true,
  morecomment=[l]{//},
  morecomment=[n]{/*}{*/},
  morestring=[b]",
  morestring=[b]',
  morestring=[b]"""
}

\usepackage{color}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
 
% Default settings for code listings
\lstset{frame=tb,
  language=scala,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  frame=single,
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}


\usetheme[secheader]{Boadilla}
\usefonttheme[onlylarge]{structurebold}
\setbeamerfont*{frametitle}{size=\normalsize,series=\bfseries}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{mini frames}[box]
\setbeamertemplate{sections/subsections in toc}[square]
\setbeamertemplate{blocks}[rounded][shadow=true]
\setbeamertemplate{bibliography item}[text]

\setbeamercolor{lightorange}{fg=black,bg=orange!40}
\setbeamercolor{lightblue}{fg=black,bg=blue!30}

\newenvironment{colorblock}[2]
{\setbeamercolor{item}{fg=#1,bg=#1}\begin{beamerboxesrounded}[upper=#1,lower=#2,shadow=true]}
  {\end{beamerboxesrounded}}



% Setup TikZ

\usepackage{tikz}
\usetikzlibrary{arrows}
\tikzstyle{block}=[draw opacity=0.7,line width=1.4cm]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newtheorem{observation}[theorem]{Observation} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Cluster Schedulers}
% \subtitle{Introduction}
\author{Pietro Michiardi}
\institute{Eurecom}
\date


\begin{document}

\begin{frame}
  \titlepage
\end{frame}


\section{Introduction}
\begin{frame}
 \begin{colorblock}{blue}{lightblue}{ }
  \begin{center}
    \Huge \textbf{\texttt{Introduction and Preliminaries}}
  \end{center}
  \end{colorblock}
\end{frame}
\input{./introduction.tex}

\begin{frame}
 \begin{colorblock}{blue}{lightblue}{ }
  \begin{center}
    \Huge \textbf{\texttt{Representative Cluster Schedulers}}
  \end{center}
  \end{colorblock}
\end{frame}

\section{YARN}
\begin{frame}
 \begin{colorblock}{blue}{lightblue}{ }
  \begin{center}
    \Huge \textbf{\texttt{YARN}}
  \end{center}
  \end{colorblock}
  \texttt{V. V. Vavilapalli, et. al., ``Apache Hadoop YARN: yet another resource negotiator'', in Proc. of ACM SOCC 2013.}

\end{frame}
\input{./yarn.tex}

\section{MESOS}
\begin{frame}
 \begin{colorblock}{blue}{lightblue}{ }
  \begin{center}
    \Huge \textbf{\texttt{Mesos}}
  \end{center}
  \end{colorblock}
  \texttt{B. Hindman, et. al., ``Mesos: a platform for fine-grained resource sharing in the data center'', in Proc. of USENIX NSDI 2011.}
\end{frame}
\input{./mesos.tex}

\section{BORG}
\begin{frame}
 \begin{colorblock}{blue}{lightblue}{ }
  \begin{center}
    \Huge \textbf{\texttt{Borg}}
  \end{center}
  \end{colorblock}
  \texttt{A. Verma, et. al., ``Large-scale cluster management at Google with Borg'', in Proc. of ACM EUROSYS, 2015.}
\end{frame}
\input{./borg.tex}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}
